Towards Spherical Robots For Mobile Mapping In Human Made Environments\tnoteref{mytitlenote}

### 2021-05-13 Latex/sections/realData.tex
Changed Cylon Setup image
Added minor infos to cylon hardware

The dataset is collected by a line scanner, in particular a SICK LMS141 industrial scanner, inside a sphere of a diameter of \SI{20}{\centi\meter} that lies on a floating desk, which is air-pressurized, such that the sphere is hovering.
On this floating desk, the sphere can rotate freely about all axis while being fixed in position. 
Hence, in this experiment the optimization space can be reduced to a rotation.
Further, without the motion, the 2D laser cannot obtain a 3D model from the environment, thus requiring registration. 
The sphere is equipped with a low-cost IMU, i.e., a PhidgetSpatial Precision 3/3/3, to estimate the orientation.

Figure~\ref{fig:float-sat-sphere} shows the experimental setup. TThe left column of figure~\ref{fig:cylon-corrected} shows the pre-registered resulting point cloud . 
We see that the point cloud is rather noisy, and in particular, the walls are sensed multiple times, hence appearing very blurry.

\begin{figure}
	\centering
	\begin{minipage}[c]{0.45\textwidth}
		\centering
		\includegraphics[width=0.33\textwidth, height=0.33\textwidth]{./images/sphere-frame-1.eps}\hfill
		\includegraphics[width=0.33\textwidth, height=0.33\textwidth]{./images/sphere-frame-2.eps}\hfill
		\includegraphics[width=0.33\textwidth, height=0.33\textwidth]{./images/sphere-frame-3.eps}\\
		\includegraphics[width=0.33\textwidth, height=0.33\textwidth]{./images/sphere-frame-4.eps}\hfill
		\includegraphics[width=0.33\textwidth, height=0.33\textwidth]{./images/sphere-frame-5.eps}\hfill
		\includegraphics[width=0.33\textwidth, height=0.33\textwidth]{./images/sphere-frame-6.eps}\hfill
	\end{minipage}\\
	\vspace{0.1cm}
	\begin{minipage}[c]{0.45\textwidth}
		\centering
		\includegraphics[width=0.4615\textwidth, trim={20cm 0 10cm 0}, clip]{./images/cylon-exploded}\hfill
		\includegraphics[width=0.525\textwidth, trim={25cm 7.5cm 15cm 5cm}, clip]{./images/cylon-setup}\hfill
	\end{minipage}
	\caption{Data acquisition using floating sphere. Top: A sequence of orientations the sphere assumes during data acquisition. Bottom: Hardware setup of the sphere.} 
	\label{fig:float-sat-sphere}
\end{figure}

>>>>

The dataset is collected by a line scanner, in particular a SICK LMS141 industrial scanner, inside a sphere of a diameter of \SI{20}{\centi\meter} that lies on a floating desk, which is air-pressurized, such that the sphere is hovering.
On this floating desk, the sphere can rotate freely about all axis while being fixed in position. 
Hence, in this experiment the optimization space can be reduced to a rotation.
Further, without the motion, the 2D laser cannot obtain a 3D model from the environment, thus requiring registration. 
The sphere is equipped with a low-cost IMU, i.e., a PhidgetSpatial Precision 3/3/3, to estimate the orientation, a battery pack and a raspberry pie for processing.

Figure~\ref{fig:float-sat-sphere} shows the experimental setup. The left column of figure~\ref{fig:cylon-corrected} shows the pre-registered resulting point cloud . 
We see that the point cloud is rather noisy, and in particular, the walls are sensed multiple times, hence appearing very blurry.

\begin{figure}
	\centering
	\begin{minipage}[c]{0.45\textwidth}
		\centering
		\includegraphics[width=0.33\textwidth, height=0.33\textwidth]{./images/sphere-frame-1.eps}\hfill
		\includegraphics[width=0.33\textwidth, height=0.33\textwidth]{./images/sphere-frame-2.eps}\hfill
		\includegraphics[width=0.33\textwidth, height=0.33\textwidth]{./images/sphere-frame-3.eps}\\
		\includegraphics[width=0.33\textwidth, height=0.33\textwidth]{./images/sphere-frame-4.eps}\hfill
		\includegraphics[width=0.33\textwidth, height=0.33\textwidth]{./images/sphere-frame-5.eps}\hfill
		\includegraphics[width=0.33\textwidth, height=0.33\textwidth]{./images/sphere-frame-6.eps}\hfill
	\end{minipage}\\
	\vspace{0.1cm}
	\begin{minipage}[c]{0.45\textwidth}
		\centering
		\includegraphics[width=0.4615\textwidth, trim={20cm 0 10cm 0}, clip]{./images/cylon-exploded}\hfill
		\includegraphics[width=0.525\textwidth]{./images/cylon_setup}\hfill
	\end{minipage}
	\caption{Data acquisition using floating sphere. Top: A sequence of orientations the sphere assumes during data acquisition. Bottom: Hardware setup of the sphere.} 
	\label{fig:float-sat-sphere}
\end{figure}
